AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-09-30 Paper/main.tex
9-30 paper

For encoding process, we use the complementary base to represent the original base in sgRNA, as others do. 
Further, we use one-hot encode strategy, which's is to say, we encoding each base in sgRNA into a four-dimensional vector 
(encode A,T,G,C into [1,0,0,0], [0,1,0,0], [0,0,1,0], [0,0,0,1], respectively), called one-hot vector. 
Then a sgRNA can be considered as a matrix $X_{oh}\in\mathbb{R}^{L\times 4} $, named one-hot matrix (a little sparse, since an one-hot vector is zero in all but one dimension). 
We believe it is meaningful to regard $X_{oh}$ as a binary image, 
therefore, it is used as an input of convolutional neural network, which performs well in the image field.
Meanwhile, as mentioned above, one-hot matrix is a little sparse.

@@

\begin{figure}[!tpb]%figure2
    \centerline{\includegraphics[scale=0.15]{newcnn.png}}
    \caption{Two categories of the deep learning models used in sgRNA related task. 
    (a) Model work in spatial domain. (b) Model work in temporal domain.}\label{fig:02}
\end{figure}
As Figure~1\vphantom{\ref{fig:02}} show,

@@

@@

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text

@@

\begin{figure}[!tpb]%figure1
\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{200pt} \vbox to 100pt{\vfill\hbox to
200pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
\end{minipage}}
\caption{Caption, caption.}\label{fig:02}
\end{figure}

>>>>

For encoding process, we use the complementary base to represent the original base in sgRNA, as others do. 
Further, we use one-hot encode strategy, which's is to say, we encoding each base in sgRNA into a four-dimensional vector 
(encode A,T,G,C into [1,0,0,0], [0,1,0,0], [0,0,1,0], [0,0,0,1], respectively), called one-hot vector. 
Then a sgRNA can be considered as a matrix $X_{oh}\in\mathbb{R}^{l\times4} $, named one-hot matrix (a little sparse, since an one-hot vector is zero in all but one dimension). 
We believe it is meaningful to regard $X_{oh}$ as a binary image, 
therefore, it is used as an input of convolutional neural network, which performs well in the image field.
Meanwhile, as mentioned above, one-hot matrix is a little sparse.

@@

\begin{figure}[!tpb]%figure2
    \centerline{\includegraphics[scale=0.15]{CNNv2.png}}
    \caption{The architecture of spatial domain method in AttCRISPR. 
    The input of the method is encoded sgRNA sequence, a $21\times 4$ one-hot matrix. 
    Then refine it through a spatial attention module, which could tell us the importance of a specific matrix element (or just say, pixel).
    Finally, a simple convolutional neural network is applied.}\label{fig:02}
\end{figure}
As Figure~2\vphantom{\ref{fig:02}} show, method in spatial domain relies on the convolutional neural network. 
As previously mentioned, sgRNA sequence has been encoded into a $21\times 4$ one-hot matrix $X_{oh}$, and we regard $X_{oh}$ as a binary image. 
Then, convolution kernels with different size are used to extract potential spatial features just like what other do in computer vision. 
According to the foregoing, the Spatial Attention Module proposed by \citeauthor{woo2018cbam:} can be applied in our method in spatial domain, 
which was used to improve the performance of CNN in vision tasks.

\begin{figure}[!tpb]%figure3
    \centerline{\includegraphics[scale=0.37]{spatialmodule.png}}
    \caption{Details of spatial attention module. A convolution layer is used to generate multi-channel map from $X_{oh}$.
    Then concatenated the output of both max-pooling and average-pooling method and forward it to the last convolution layer.
    A sigmoid is used to map the final result to a range of zero to one.
    }\label{fig:03}
\end{figure}

As Figure~3\vphantom{\ref{fig:03}} show, Given an one-hot map $X_{oh}$, spatial attention module generating spatial attention matrix 
$M_s\in\mathbb{R}^{l\times 4}$ with the same as $X_{oh}$ in shape. 
Each element of $M_s$ is constrained to a range of zero to one, implemented by a sigmoid function, which reflects the importance of the corresponding elements of $X_{oh}$.
The overall spatial attention process can be summarized as:
\begin{equation}
X_{mc} = f^{3\times4}(X_{oh})\label{eq:09}\vspace*{-10pt}
\end{equation}

\begin{equation}
M_s = \sigma(f^{3\times2}([AvgPool(X_{mc});MaxPool(X_{mc})]))\label{eq:10}\vspace*{-10pt}
\end{equation}

\begin{equation}
X_{rf} = M_s\otimes X_{oh}\label{eq:11}\vspace*{-10pt}
\end{equation}\\

where $f^{p\times q}$ represents a convolution operation with the filter size of $p\times q$, 
$p,q\in\mathbb{Z}^{+}$, $X_{mc}$ is a multi-channel map generated by $X_{oh}$, $\sigma$ denotes the sigmoid function, 
AvgPool denotes the average-pooling operation, MaxPool denotes the max-pooling operation, $\otimes$ denotes element-wise multiplication.

Spatial attention matrix $M_s$ formally conforms to our proposed definition of first-order preference (each element of $X_{oh}$ is multiplied by the corresponding element of $M_s$), 
in other word, element of $M_s$ reveal how important the corresponding elements in $X_{oh}$ is. 
We think it can reveal the preference of the scoring function at each position. 
For instance, follow the encoding rules above, train spatial domain part of AttCRISPR with the WT-SpCas9 dataset. 
Then take the average of all spatial attention matrix, and the element in the first row and third column are closer to 1, which means when calculate the final score, 
G typically may have a important contribution at first position within sgRNA sequence. 
In fact, this corresponds to some early studies concerning the Human (hU6) promoter, which is believed to require G as the first nucleotide of its transcript \citep{cong2013multiplex,jinek2012a,mali2013rnaguided}.

@@

\begin{figure}[!tpb]%figure4
    \centerline{\includegraphics[scale=0.15]{CNNv2.png}}
    \caption{The architecture of temporal domain method in AttCRISPR. 
    The input of the method is embedding sgRNA sequence, a $21\times e$ embedding matrix, where $e$ is the dimension of a nucleotide embedding vector. 
    }\label{fig:04}
\end{figure}
As Figure~4\vphantom{\ref{fig:04}} show, method in temporal domain relies on the recurrent neural network (or its variant). 
As previously mentioned, we mapping each one-hot vector into a dense real-valued high-dimensional space follow the Equation~(\ref{eq:08}), which generates the embedded matrix $X_e$.
And we regard $X_{e}$ as a sequential data, or temporal data.
Recurrent neural network (or its variant) has showed outstanding performance in the tasks with temporal data (for instance, natural language processing, sequential recommendation). 
That's why we prefer to use it to extract potential temporal features.

@@

@@
